Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-27 paper.qmd
Figure 4 fixed the grid, then according to the data this not going to change

```{r}
#| label: code-illustration
# Code to draw illustration for notation
start_pt <- all_centroids_df |> 
  filter(hexID == 1)
d_rect <- tibble(x1min = 0, 
                 x1max = 1,
                 x2min = 0,
                 x2max = r2)

@@

a1 <- tibble(x = all_centroids_df$c_x[4],
             xend = all_centroids_df$c_x[5],
             y = all_centroids_df$c_y[21],
             yend = all_centroids_df$c_y[21],

@@

a2 <- tibble(x = all_centroids_df$c_x[25],
             xend = all_centroids_df$c_x[25],
             y = all_centroids_df$c_y[25],
             yend = all_centroids_df$c_y[33],

@@

    geom_polygon(data = hex_grid, 

@@

    geom_point(data = all_centroids_df, aes(

@@

trimesh_two_curvy_removed1_with_data <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy3,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#000000",
            alpha = 0.5) +
  interior_annotation("b")

>>>>

```{r}
#| label: code-illustration
# Code to draw illustration for notation
## hexagon binning to have regular hexagons
hb_obj_notation <- hex_binning(
  data = umap_two_curvy_scaled, 
  bin1 = 7, 
  r2 = 1.6,
  q = 0.1)

## Data set with all centroids
all_centroids_df_temp <- hb_obj_notation$centroids
hex_grid_temp <- hb_obj_notation$hex_poly

start_pt <- all_centroids_df_temp |> 
  filter(hexID == 1)
d_rect <- tibble(x1min = 0, 
                 x1max = 1,
                 x2min = 0,
                 x2max = 1.6)

@@

a1 <- tibble(x = all_centroids_df_temp$c_x[4],
             xend = all_centroids_df_temp$c_x[5],
             y = all_centroids_df_temp$c_y[21],
             yend = all_centroids_df_temp$c_y[21],

@@

a2 <- tibble(x = all_centroids_df_temp$c_x[25],
             xend = all_centroids_df_temp$c_x[25],
             y = all_centroids_df_temp$c_y[25],
             yend = all_centroids_df_temp$c_y[33],

@@

    geom_polygon(data = hex_grid_temp, 

@@

    geom_point(data = all_centroids_df_temp, aes(

@@

trimesh_two_curvy_removed1_with_data <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy3,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(data = umap_two_curvy_scaled,
             aes(
               x = UMAP1,
               y = UMAP2
             ),
             color = "#000000",
            alpha = 0.5) +
  #coord_equal() +
  interior_annotation("b")
